\documentclass{beamer}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{array}
\usepackage{booktabs}
\usepackage{hyperref}

\usetheme{default}

\title{Breast Cancer Analysis}
\author{Name}
\date{Submitted On: Feb 5, 2025}

\begin{document}

\begin{frame}
    \titlepage
\end{frame}

\begin{frame}
    \frametitle{Introduction}
    \begin{itemize}
        \item \textbf{Significance of Breast Cancer as a Global Health Issue}
              \begin{itemize}
                  \item In 2022, approximately \textbf{2.3 million women} were diagnosed with breast cancer worldwide.
                  \item This represents about \textbf{one in four} of all cancers in women.
                  \item In 2022, \textbf{670,000 women} died from breast cancer worldwide.
                  \item In 2020, breast cancer was the cause of \textbf{16\%} of cancer deaths in women.
                  \item Breast cancer incidence has increased by more than \textbf{20\%} since 2008.
                  \item Breast cancer incidence is growing in many parts of the world, especially in transitioning countries.
                  \item In 2019, \textbf{25,100 men} were diagnosed with breast cancer globally.
              \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Brief intro to types of breast cancer}

    \textbf{Benign vs. Malignant Tumors}
    \begin{center}
        \begin{tabular}{ | >{\bfseries}l | >{\raggedright\arraybackslash}p{5cm} | }
            \hline
            \textbf{Category}         & \textbf{Description}                                                                                               \\
            \hline
            \textbf{Benign Tumors}    & Non-cancerous, usually slow-growing, doesn't spread, usually not life-threatening.                                 \\
            \hline
            \textbf{Malignant Tumors} & Cancerous, can grow rapidly, invade surrounding tissues, spread to other body parts, potentially life-threatening. \\
            \hline
        \end{tabular}
    \end{center}
\end{frame}

\begin{frame}
    \frametitle{Brief intro to types of breast cancer}

    \textbf{Invasive Breast Cancers: Types}
    \begin{center}
        \begin{tabular}{ | >{\bfseries}l | >{\raggedright\arraybackslash}p{4cm} | >{\raggedright\arraybackslash}p{4cm} | }
            \hline
            \textbf{Feature}      & \textbf{Invasive Ductal Carcinoma (IDC)}         & \textbf{Invasive Lobular Carcinoma (ILC)}                                            \\
            \hline
            \textbf{Frequency}    & Most common type of breast cancer (70-80\%).     & Second most common (10-15\%).                                                        \\
            \hline
            \textbf{Origin}       & Starts in the milk ducts.                        & Starts in the milk lobules.                                                          \\
            \hline
            \textbf{Presentation} & May form a lump and may spread to other tissues. & May not typically form a lump; presents as a thickening and may affect both breasts. \\
            \hline
        \end{tabular}
    \end{center}
\end{frame}

\begin{frame}
    \frametitle{Project Motivation}
    {\LARGE
        \begin{itemize}
            \item Chose this topic because breast cancer is a major issue.
            \item Goals of the project:
                  \begin{itemize}
                      \item Analyze key datasets related to breast cancer.
                      \item Apply statistical methods to uncover significant insights.
                      \item Inform strategies for early detection and treatment.
                  \end{itemize}
        \end{itemize}
    }
\end{frame}

\begin{frame}
    \frametitle{Dataset Introduction}
    \textbf{Source of the Dataset:}\\[1ex]
    This breast cancer domain was obtained from the University Medical Centre, Institute of Oncology, Ljubljana, Yugoslavia. This is one of three domains provided by the Oncology Institute that has repeatedly appeared in the machine learning literature.
    
    \vspace{1em}
    \textbf{Citations:}\\[0.5ex]
    Zwitter, M. \& Soklic, M. (1988). Breast Cancer [Dataset]. UCI Machine Learning Repository. \href{https://doi.org/10.24432/C51P4M}{https://doi.org/10.24432/C51P4M}
    
    \vspace{1em}
    \textbf{Download Link:}\\[0.5ex]
    \href{https://archive.ics.uci.edu/dataset/14/breast+cancer}{https://archive.ics.uci.edu/dataset/14/breast+cancer}
\end{frame}

\begin{frame}
    \frametitle{Breast Cancer Diagnosis Data Preview}
    \input{tables/breast_cancer_cell_sample_part1.tex}
    \vspace{1em}
    \input{tables/breast_cancer_cell_sample_part2.tex}
\end{frame}

\begin{frame}
    \frametitle{Breast Cancer Diagnosis Data Preview (Part 3)}
    \input{tables/breast_cancer_cell_sample_part3.tex}
    \vspace{1em}
    \input{tables/breast_cancer_cell_sample_part4.tex}
\end{frame}

\begin{frame}
    \frametitle{Breast Cancer Diagnosis Data Preview (Part 4)}
    \input{tables/breast_cancer_cell_sample_part5.tex}
    \vspace{1em}
    \input{tables/breast_cancer_cell_sample_part6.tex}
\end{frame}

\begin{frame}
    \frametitle{Breast Cancer Diagnosis Data Preview (Part 5)}
    \input{tables/breast_cancer_cell_sample_part7.tex}
    \vspace{1em}
    \input{tables/breast_cancer_cell_sample_part8.tex}
\end{frame}

\begin{frame}
    \frametitle{Global Cancer Data Preview}
    \input{tables/cancers_global_sample_part1.tex}
    \vspace{1em}
    \input{tables/cancers_global_sample_part2.tex}
\end{frame}

\begin{frame}
    \frametitle{Breast Cancer Statistics by Country Preview}
    \input{tables/breast_country_sample_part1.tex}
    \vspace{1em}
    \input{tables/breast_country_sample_part2.tex}
\end{frame}

\begin{frame}
    \frametitle{Breast Cancer Continent Mortality Data Preview}
    \input{tables/breast_cancer_continent_mortality_sample_part1.tex}
    \vspace{1em}
    \input{tables/breast_cancer_continent_mortality_sample_part2.tex}
\end{frame}

\end{document}